**The Heart Lies: The Role of Interoception and Theory of Mind in Deception**

### 2022-11-07 paper/manuscript.Rmd
manu updates

In this post-truth era, deception has become increasingly prevalent in our everyday lives [@lewandowsky2017beyond]. Although the act of deceiving is complex and cognitively taxing [@abe2007deceiving], often requiring effortful self-regulation to conceal [@krokoszinski2016emotion], research shows that people tend to under-estimate their ability to successfully deceive others [@elaad2003effects]. Moreover, meta-analytic findings suggest that the ability of the liar plays a more significant role than the lie detector in deceptive interactions [@verigin2019lie; @bond2008individual; @levine2011sender]. However, relative to the abundant literature regarding deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], surprisingly little attention has been conferred to investigating the inter-individual differences in people's ability to successfully lie.

@@

As deception requires the liar to intentionally manipulate the beliefs of others [@burgoon1994interpersonal; @sip2012if], most research on lying capability has been focused on higher order cognitive processes, particularly in theory of mind (TOM). TOM refers to the ability to infer that others have mental states, such as beliefs, emotions and intentions, distinct from ourselves [@lee2021lying; @wellman2001meta; @baron1997mindblindness]. Indeed, the capacity to tell lies, as well as the complexity of lies told, have previously been found to be associated with higher TOM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role]. Furthermore, the deceptive capabilities of children is often used as a measure of their TOM abilities. However, given the view that development of TOM abilities serve as the building blocks of other higher order cognitive processes [@ketelaars2010dynamics; @isaksson2021s], studies investigating the links between TOM and lying ability have predominantly been focused on children and individuals with neurocognitive deficits [@beaudoin2020systematic; @bora2017meta; @roheger2022progression]. As such, little is known with regards to the role TOM plays in the lying ability of neurotypical adults.

<!-- Defining interoceptive processes -->

Alternatively, the variability observed in interoception, broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying]. Following @garfinkel2015knowing's three-dimensional framework, interoception is comprised of distinct facets, namely - *interoceptive accuracy*, the objective ability to monitor internal bodily signals; *interoceptive sensibility*, the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness*, the metacognitive awareness of one's interoceptive accuracy (i.e., accuracy-confidence correspondence).

<!-- While interoceptive sensibility may be an important component, the correspondence between the confidence and accuracy, or interoceptive awareness appears to be associated with the downregulation of emotional responses and their associated physiological symptoms [@fustos2013embodiment; @critchley2017interoception; @critchley2018influence]. -->

@@

Given the influence of interoceptive abilities on higher order cognition, particularly with regards to emotional processing  [@barrett2015interoceptive; @petzschner2021computational; @vabba2022interoceptive], it is possible that interoception bears an effect on people's capacity to tell lies. Although there has been little research investigating the links between interoception and deceptive ability *per se*, some studies have found heightened self-focus towards internal bodily signals to result in an increased demonstration of apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening]. In line with these findings, @vabba2022interoceptive reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high (relative to low), whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.

In contrast, however, the somatic marker hypothesis posits higher interoception to be associated with a propensity towards making rational decisions [@damasio1996somatic]. Indeed, previous research has shown a negative correlation between interoceptive awareness and the likelihood to make risky decisions [@dunn2010listening; @furman2013interoceptive]. Taking these mixed findings to perspective with the lack of consideration for the multidimensional nature of interoception in past studies, as well as the paucity in research linking deceptive ability with interoception, more studies are warranted to examine the relationship between interoception and deception.

@@

This study aims at exploring the relationship between TOM and interoception with deceptive ability. Despite the criticism surrounding the somatic marker hypothesis [@dunn2006somatic; @maia2004reexamination], interoception has been shown to be associated with goal-directed behaviours and positively influence rational decision-making in ambiguous situations [@poppa2018somatic; @naqvi2014insula; @avery2017brain]. As such, we expect individuals higher in interoception to exhibit better lying ability, as indicated by higher lie confidence, lower physiological arousal and shorter response time in the polygraph condition. In the interrogation condition, we expect people with higher TOM abilities to exhibit be better at lying, as indicated by higher low confidence, lower physiological arousal and shorter response time.

@@

The plan for this study was preregistered **(OSF?)**.

@@

30 participants were recruited through  posters, flyers, and online social media platforms. Inclusion criteria included residing in Singapore, and an absence of current or history of neurological, psychiatric, or cardiovascular disorders. 4 participants were excluded as a result of a technical error that led to their data not being recorded. The final sample consists 26 participants (Mean age = 20.9, SD = 2.0, range:[18, 25], Sex: 65.4% women, 34.6% men, 0.00% non-binary). The heart rate of one participant and response time of one participant were excluded from analysis due to extreme outlying values [**PLEASE HELP ME CONFIRM**].

@@

The *Basic Empathy Scale (BES)* is a 20-item, 5-point Likert scale (Strongly Disagree - Stongly Agree) that measures cognitive and affective empathy [@jolliffe2006development]. Although TOM and empathy are regarded as distinct psychological constructs, abundant evidence points to them being closely related [@gallant2020developing; @sebastian2012neural], with empathy thought to be integrated in the affective dimension of TOM (i.e., the ability to infer what someone else is feeling) [@shamay2010role]. The *Yoni Task*, which comprises 3 dimensions, namely cognitive, physical and affective, was also administered to assess participants' objective TOM ability [@shamay2007dissociable].

@@

To measure interoceptive accuracy, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart] while having their heart beats recorded. During the HCT task, participants were instructed to count the number of heart beats they felt over 5 varying time periods (20s, 25s, 30s, 35s, 40s) administered in a randomized order. After each time period, interoceptive sensibility was assessed by having participants respond how confident they were of their counting accuracy using a visual analog scale. Furthermore, participants also completed the *MAIA-2 questionnaire* [@mehling2012multidimensional], a 32-item scale that measures 8 dimensions of interoception (Noticing, Not-Distracting, Not-Worrying, Attention, Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust) using a 5-point Likert scale(Never-Always).

@@

We used the *LIE Scale*, a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency) on a visual analog scale (Disagree-Agree) [@makowski2021structure].

@@

We designed a computerized directed-lying experimental paradigm (the *Deception Task*) to assess participants' lying ability in different scenarios. Each *Deception Task* trial is comprised of a question presented on a computer screen with an accompanying instruction that either asked participants to verbally lie or tell the truth. The instructions for each trial were displayed for a maximum of 10 seconds, or until the participants responded. Notably, these questions were either phrased directly (*"What is your favourite sport?*) or indirectly (*"Is your favourite sport Hockey?"*). The *Deception Task* paradigm consists of 2 conditions - namely, the *Interrogation Condition* and the *Polygraph Condition*.

In the **Interrogation Condition**, social feedback in the form of a video stream with an examiner was presented to participants during each trial. Participants were informed that the examiner would be evaluating the truthfulness of their responses by observing through the live video feed, when in actuality, the video was a pre-recorded video clip of a confederate. This was done to heighten the salience of social cues so as to facilitate participants' TOM abilities.

In the *Polygraph condition*, cardiac feedback in the form of an electrocardiogram (ECG) was presented to participants during each trial Participants were informed that they were being shown live feedback of their own physiological signals when in fact, the displayed ECG was of a prerecorded video clip. This was done in order to heighten the salience of interoceptive cues and facilitate participants' interoceptive abilities.

Following each response, participants were asked to rate their confidence in the success of their truth or lie-telling before progressing to the next trial.

@@

In the first phase of the study, participants answered a brief demographic survey before being administered a battery of questionnaires (*BES*, *MAIA-2*, *Lie Scale*) and cognitive-behavioural tasks (*HCT*, *Yoni Task*). This series of tasks and questionnaires were administered in a randomized order [**TBC**] in order to ensure there were no order effects. In the second phase of the study, the *Deception Task* paradigm was presented to participants. Similar to the first phase, the order sequence of the 2 conditions (*polygraph* vs *interrogation*) was randomized [**TBC**], with each condition comprising 20 trials. In total, each participant underwent 40 *Deception Task* trials, of which they had to respond with either lies or truths depending on the given instruction.

Physiological recording devices were prepared prior to beginning the experimental paradigm. Using three ECG electrodes placed according to a modified Lead II configuration [@takuma1995alternative], cardiovascular activity was recorded via the BioPac MP160 system (BioPac Systems Inc., USA) and the AcqKnowledge 5.0 software. Events were marked by a photosensor attached to the screen.

@@

The manipulation checks consist of testing whether there is an effect of question phrasing (direct vs. indirect), and condition (polygraph *vs.* interrogation), on our 3 outcome variables: the participants' ratings of confidence that their answers (lies *vs.* truths) were convincing, the response time (RT), and the heart rate change associated with the response. This analysis was performed using mixed models with the participants and questions both entered as random factors. Marginal contrasts analysis was also performed to clarify the differences between conditions. To allow for a better quantification of the uncertainty associated with the effects, as well increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework [@makowski2019bayestestr], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).

To further counterbalance the low number of participants and maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, theory of mind and interoception). We used factor analysis (using the method agreement procedure to estimate the optimal number of dimensions, **REF PARAMETERS PKG**), rather PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained. Then, we modeled the relationship between these inter-individual composite scores (the analysis for all the variables is included in Supplementary Materials) and the 3 outcome variables in interaction with the condition (polygraph *vs.* interrogation). Finally, we also investigated the relationship between the deception scale traits, and the theory of mind and interoception scores using Bayesian correlations.

@@

The composite *TOM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67%\%$), specifically in the polygraph condition. No significant effect was found heart rate, and no correlation with the deception scale traits.

@@

The *Listening* interoception score was significantly associated with an increased confidence in lies, in the polygraph ($\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%$) and interrogation condition ($\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%$). It was also associated with faster answers, particularly for lies ($\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%$) and truths ($\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%$) in the polygraph condition. No significant association was found with heart rate. This score also correlated with the deception *Contextuality* trait ($r = 0.50,~95\%~CI~[0.04, 0.64],~BF_{10} = 3.48\%$).

The *Focus* interoception score was significantly associated with an increased confidence in truthful responses in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$) and interrogation condition ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76%\%$). No significant association was found with RT or heart rate, but the score correlated with the deception *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$).

@@

This study aimed to examine the relationship between TOM and interoception on deceptive ability. Whereas there lies an abundance of deception literature associated with social cognition and emotion regulation, most of the research had been focused on deception detection, leaving a paucity in the studies pertaining to lying ability. Through our bimodal feedback *Deception Task* paradigm, our results found a significant positive correlation between interoception and confidence in one's own lies. This is not only in line with @murphy2019classifying's findings on interoceptive awareness and interoceptive sensibility, but also extends their influence to other high order cognitve processes such as lying

>>>>

In this post-truth era, deception has become increasingly prevalent in our everyday lives [@lewandowsky2017beyond]. Although the act of deceiving is regarded as complex and often requires effortful self-regulation to conceal [@abe2007deceiving; @krokoszinski2016emotion], research shows that people tend to under-estimate their ability to successfully lie [@elaad2003effects]. However, relative to the abundant literature regarding deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], surprisingly little attention has been conferred to investigating the inter-individual differences in people's ability to lie. Given meta-analytic findings wherein the deceptive ability of the liar is suggested to be more important than the lie detector in deceptive interactions [@verigin2019lie; @bond2008individual; @levine2011sender], it is perhaps more pertinent to investigate what makes someone a better liar.

@@

As deception requires the liar to intentionally manipulate the beliefs of others [@burgoon1994interpersonal; @sip2012if], most research on lying capability has been focused on higher order cognitive processes, particularly in theory of mind (TOM). TOM refers to the ability to infer that others have mental states, such as beliefs, emotions and intentions, distinct from ourselves [@lee2021lying; @wellman2001meta; @baron1997mindblindness]. Indeed, the capacity to tell lies, as well as the complexity of lies told, have previously been found to be related to higher TOM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role]. Furthermore, the deceptive capabilities of children is often used as a measure of their TOM abilities. However, studies investigating the links between TOM and lying ability have predominantly been focused on children and individuals with neurocognitive deficits [@beaudoin2020systematic; @bora2017meta; @roheger2022progression]; likely a result of the view of TOM as the foundation of other higher order cognitive processes [@ketelaars2010dynamics; @isaksson2021s]. As such, little is known regarding the role TOM plays in the lying ability of healthy adults.

@@

Alternatively, differences in interoception could also be a factor worthy of consideration. Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].

Given the established link between interoceptive abilities and emotional processing [@barrett2015interoceptive; @petzschner2021computational; @vabba2022interoceptive], it is possible that interoception bears influence on people's capacity to tell lies. Although there has been little research investigating the relationship between interoception and deceptive ability *per se*, some studies have found heightened self-focus towards internal bodily signals to be associated with an increased demonstration of apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening]. In line with these findings, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high (relative to low), whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told.

In contrast, previous decision-making studies have shown a negative correlation between interoceptive awareness and one's likelihood of making risky decisions [@dunn2010listening; @furman2013interoceptive]. In fact, this is consistent with the somatic marker hypothesis, which posits interoception to be associated with a propensity towards making rational decisions [@damasio1996somatic]. While the literature pertaining to interoception seems contradictory, it is possible that these mixed findings are a result of a failure to take into consideration interoception's multidimensionality. According to @garfinkel2015knowing's three-dimensional framework, interoception is comprised of three distinct facets, namely - *interoceptive accuracy*, the objective ability to monitor internal bodily signals; *interoceptive sensibility*, the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness*, the metacognitive awareness of one's interoceptive accuracy (i.e., accuracy-confidence correspondence). However, previous interoception research has largely been focused on interoceptive accuracy [@wallman2021physical]. Taking this to perspective with the paucity in studies linking deceptive ability with interoception, more studies are warranted to comprehensively examine the relationship between interoception and deception.

@@

The aim of the present study was to explore the interplay effects of TOM and interoception on individuals' deceptive ability, as indicated by their lie confidence, physiological arousal and response time. To this end, we designed a directed-lying bi-modal feedback paradigm comprising 2 conditions ( *Interrogation* vs *Polygraph*) with distinct feedback cues. In particular, salient social feedback cues were conferred during the *Interrogation condition*, whereas physiological feedback cues were given during the *Polygraph condition*. We expected interoception to positively predict lying ability in the *Polygraph condition*, and have no significant effect on one's ability to lie in the *Interrogation condition*. Similarly, we hypothesized that TOM would positively predict individuals' capability in lying in the *Interrogation condition* and exhibit non-significant effects in the *Polygraph condition*.

@@

@@

30 participants were recruited through  posters, flyers, and online social media platforms. Inclusion criteria included residing in Singapore, and an absence of current or history of neurological, psychiatric, or cardiovascular disorders. 4 participants were excluded as a result of a technical error that led to their data not being recorded. The final sample consists 26 participants (Mean age = 20.9, SD = 2.0, range:[18, 25], Sex: 65.4% women, 34.6% men, 0.00% non-binary). The heart rate of one participant and response time of one participant were excluded from further analysis due to extreme outlying values [**PLEASE HELP ME CONFIRM**].

@@

The *Basic Empathy Scale (BES)* is a 20-item, 5-point Likert scale (Strongly Disagree - Strongly Agree) that measures cognitive and affective empathy [@jolliffe2006development]. Although TOM and empathy are regarded as distinct psychological constructs, previous research findings point to them being closely related [@gallant2020developing; @sebastian2012neural]. Specifically, empathy is often thought to be an integral component in the affective dimension of TOM (i.e., the ability to infer what someone else is feeling) [@shamay2010role]. The *Yoni Task*, which comprises 3 dimensions, namely cognitive, physical and affective, was also administered to assess participants' objective TOM ability [@shamay2007dissociable].

@@

To assess particpants' interoceptive ability, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart] while having their actual heartbeats recorded. During the HCT task, participants were instructed to count the number of heartbeats they felt over 5 trials with varying time intervals (20s, 25s, 30s, 35s, 40s), the sequence of which was randomized. Interoceptive accuracy (*HCT Accuracy*) was then computed based on the absolute difference between the actual number of heartbeats and the number of heartbeats counted during each trial. To assess their interoceptive sensibility (*HCT Confidence*), participants were asked to indicate, on a visual analog, how confident they were of their heartbeat counting accuracy at the end of each trial.

The *MAIA-2* [@mehling2012multidimensional], a 32-item questionnaire which measures 8 dimensions of interoception (Noticing, Not-Distracting, Not-Worrying, Attention, Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust) using a 5-point Likert scale (Never-Always) was also administered.

@@

To evaluate participants' tendency to lie in their everyday lives, we used the *LIE Scale*, a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency) on a visual analog scale (Disagree-Agree) [@makowski2021structure].

@@

We designed a computerized directed-lying experimental paradigm (the *Deception Task*) consisting of 2 conditions (the *Interrogation Condition* and the *Polygraph Condition*) to assess participants' lying ability.

In the **Interrogation Condition**, participants' response to each trial was followed by social feedback in the form of a video stream with an examiner. Notably, participants were informed that the examiner would be evaluating the truthfulness of their responses by observing them through the live video feed. In actuality, the video was a pre-recorded video clip of a confederate, and the same video-clip was presented to all participants.

In the *Polygraph condition*, participants' response to each trial was followed by physiological feedback in the form of an electrocardiogram (ECG) instead. Specifically, participants were informed that they were being shown live feedback of their own physiological signals when in fact, the displayed ECG was that of a pre-recorded video clip. Similar to the *Interrogation Condition*, all participants were shown the same pre-recorded video clip of an electrocardiogram.

Regardless of the task condition, participants were presented with a question, either phrased directly (*"What is your favourite sport?*), or indirectly (*"Is your favourite sport Hockey?"*), on a computer screen with accompanying instructions that either asked participants to verbally lie or tell the truth following each *Deception Task* trial. These instructions were displayed for a maximum of 10 seconds, or until the participants responded. Following each response, participants were then asked to rate their confidence in how convincing their answer was, before progressing to the next trial.

@@

In the first phase of the study, participants answered a brief demographic survey before being administered a battery of questionnaires (*BES*, *MAIA-2*, *Lie Scale*) and cognitive-behavioural tasks (*HCT*, *Yoni Task*). This series of tasks and questionnaires were administered in a randomized order [**TBC**] in order to control for order effects. In the second phase of the study, the *Deception Task* paradigm was presented to participants. Similar to the first phase, the order sequence of the 2 conditions (*polygraph* vs *interrogation*) was randomized [**TBC**], with each condition comprising 40 trials. Within each condition, participants were instructed to lie in half of the trials (20 truth trials; 20 lie trials). In total, each participant underwent 80 *Deception Task* trials, of which they had to respond with either lies or truths depending on the given instruction.

Physiological recording devices were prepared prior to beginning the experimental paradigm. Using three ECG electrodes placed according to a modified Lead II configuration [@takuma1995alternative], cardiovascular activity, sampled at 1000Hz (**TBC**) was recorded via the BioPac MP160 system (BioPac Systems Inc., USA) and the AcqKnowledge 5.0 software. Events were marked by a photosensor attached to the screen.

@@

The manipulation checks consist of testing whether there is an effect of question phrasing (direct vs. indirect), and condition (polygraph *vs.* interrogation), on our 3 outcome variables: the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT), and the heart rate change associated with the response. This analysis was performed using mixed models with the participants and questions both entered as random factors. Marginal contrasts analysis was also performed to clarify the differences between conditions. To allow for a better quantification of the uncertainty associated with the effects, as well as increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework [@makowski2019bayestestr], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).

To further counterbalance the low number of participants and maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, TOM and interoception). We favoured the use of factor analysis (using the method agreement procedure to estimate the optimal number of dimensions, @parametersArticle), over PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained. Then, we modeled the relationship between these inter-individual composite scores (the analysis for all the variables is included in Supplementary Materials) and the 3 outcome variables in interaction with the condition (polygraph *vs.* interrogation). Finally, we also investigated the relationship between the deception scale traits, and the theory of mind and interoception scores using Bayesian correlations.

@@

The composite *TOM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67%\%$), specifically in the polygraph condition. No significant effect was found with regards to heart rate, and no correlation was observed with dispositional lying traits.

@@

The *Listening* interoception score was significantly associated with an increased confidence in lies, in the polygraph ($\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%$) and interrogation condition ($\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%$). It was also associated with faster answers, particularly for lies ($\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%$) and truths ($\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%$) in the polygraph condition. No significant association was found with heart rate. This score also correlated with the dispositional lying *Contextuality* trait ($r = 0.50,~95\%~CI~[0.04, 0.64],~BF_{10} = 3.48\%$).

The *Focus* interoception score was significantly associated with an increased confidence in truthful responses in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$) and interrogation condition ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76%\%$). No significant association was found with RT or heart rate, but the score correlated with the dispositional lying *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$).

@@

While there is extensive literature associating deception with social cognition and emotion regulation, most of such research had been focused on deception detection, leaving a paucity in the studies pertaining to lying ability. This study hence seeks to address this research gap, further aiming to examine the interplay effect of TOM and interoception on deceptive ability. Using a bi-modal feedback deception task paradigm, participants were found to report significantly lower lie confidence in the *Polygraph condition*, relative to the *Interrogation condiiton*. Notably, we also found a significant association between several facets of interoception with individuals' lie confidence and response time in the polygraph condition. Taken together, this could be suggestive of people's greater reliance on social feedback cues when telling lies
